### 2016-09-02 lineups.Rnw
add more description of lineups and how they were chosen

\subsection{Methods}
In order to test our hypothesis, we set up an amazon turk experiment using the lineup protocal of {\color{green} Buja et all (2009). FIX CITE}. We presented four types of lineups: M1 v. M2, M2 v. M1, M1 v. M3, and M3 v. M1, where M1, M2, and M3 have the objective functions givein in ~\ref{tab:models}. For each lineup, there were 12 plots shown: 11 of the plots were simulated from the first model (the ``null" model) and 1 was simulated from the second model (the ``alternative" model). The order of the plots in the lineups was randomly assigned.

>>>>

\subsection{Methods}
In order to test our hypothesis, we set up an Amazon Mechanical Turk experiment (~\cite{turk}) using the lineup protocal of ~\cite{Bujaetal}. We presented four types of lineups: M1 v. M2, M2 v. M1, M1 v. M3, and M3 v. M1, where M1, M2, and M3 have the objective functions given in ~\ref{tab:models}. We created a total of 25 lineups to show to Amazon Turk users taking our experiment: 10 for M1 v. M2 and 5 each for the other three types of lineups. In each lineup, there were 12 plots shown: 11 of the plots were simulated from the first model (the ``null" model) and 1 was simulated from the second model (the ``alternative" model). We chose to show lineups of size 12 because we felt that showing more than 12 would be too large of a cognitive load, while showing fewer than 12 would leave too much of the experiment to random chance. The order of the plots within the lineups was randomly assigned. We selected five lineups presented from each group based on the following criteria: first, for M1 v M2 and M1 v M3, we selected the lineups where the additional parameter in the objective function, $\beta_3$ and $\beta_4$, respectively, had the largest estimated value among the 12 networks presented. There were not many of these in the size 12 lineups, so our other selection criteria was that the estimated parameter value was larger in the alternative panel than in at least half of the other lineups and it was close to the estimate from the panel that did have the largest value. For the M2 v were chosen where the smallest parameter estimate belonged to the alternative model. If there more lineups were needed, we next selected those which had estimates smaller than at least half of the other panels and were close to the minimum estimate in the lineup. For the remaining five plots of type M1 v M2, we chose the lineups where the alternative plot had the largest number of jumping transitive triplets appear in the network. We chose this  statistic because its value has great effect on both the estimation of the $\beta_3$ parameter and on the visual appearance of the plot.
